\papertitle

### 2014-03-20 final-report/paper.tex
network vis 2 caption
Thierry and I fixed numbering scheme. Other small fixes

This paper introduced \system, a visualization tool carefully tailored to help
database developers or users to quickly identify common distributed databases
performance bottlenecks, like tail latencies, data skew, etc. Our tool has been
successfully integrated with the Myria distributed database system, and has already
been used to identify several bugs, like poor physical query plan optimization,
tail latencies, poor data partitioning. We believe the visualization techniques
we used are appropriate to help the user quickly navigate to/find the cause of the
performance problem. \system could be easily plugged-in with another
distributed database system, the only requirement being a specific log data
format.

>>>>

This paper introduced \system, a visualization tool carefully tailored to help
database developers or users to quickly identify common distributed databases
performance bottlenecks, like tail latencies, data skew, etc. Our tool has been
successfully integrated with the Myria distributed database system, and has already
been used to identify several bugs, like poor physical query plan optimization,
tail latencies, poor data partitioning, which led us to believe the
visualization techniques we used are appropriate to help the user quickly
navigate to/find the cause of the performance problem. \system could be easily
plugged-in with another distributed database system, the only requirement being
a specific log data format.
